Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
e3

\paragraph{Unbalanced tree search} We ran UTS-mem with a geometric 100M-vertex tree
(T1L). Figure~\ref{fig:uts_compare} shows the performance in terms of
number of vertices visited per second versus number of compute
nodes. Grappa is 3.2 times faster than the XMT at 16 nodes.

@@

We ran BFS on a synthetic Kronecker graph with $2^{25}$ vertices and
$2^{29}$ edges (25 GB of data). Figure~\ref{fig:bfs-performance} shows
our performance in terms of graph edges traversed per second. The XMT
is 2.5 times faster than Grappa at 16 nodes.

>>>>

\paragraph{Unbalanced tree search} We ran UTS-mem with a geometric 100M-vertex tree
(T1L). Figure~\ref{fig:uts_compare} shows the performance in terms of
number of vertices visited per second versus number of compute
nodes. Grappa is 3.2 times faster than the XMT at 16 nodes.  As we will show later, the performance advantage Grappa has over XMT increases as more nodes are added.  The main reason Grappa performs better is the software-based delegate synchronization obviates the need for the retry-based synchronization that XMT uses.

@@

We ran BFS on a synthetic Kronecker graph with $2^{25}$ vertices and
$2^{29}$ edges (25 GB of data). Figure~\ref{fig:bfs-performance} shows
our performance in terms of graph edges traversed per second. The XMT
is 2.5 times faster than Grappa at 16 nodes.  Performance does scale at a constant rate for Grappa, suggesting that adding more nodes will increase performance.
